In contrast to a non-synchronous  regulator, our design uses two complementary
MOSFETs $V_2$ and $V_3$ (in the middle of Figure \ref{fig:circuit:buck} on the
fold-out) , whereby $V_3$ acts as  an active replacement for the free wheeling
diode  typically found  in  non-synchronous designs. As  mentioned earlier,  a
crucial feature of  this device is the ability to  \emph{absorb} power.  $V_3$
does this by regulating current in the opposite direction through the inductor
$L_1$.

When  selecting  switching  MOSFETs,  the  following  parameters are critical in
determining the best devices for a given application: $Q_G$ (Total Gate Charge),
$R_{DS_{(on)}}$ (On-Resistance), $Q_{GD}$ (Gate to Drain Charge), $Q_{GS}$ (Gate
to Source  Charge),  $R_G$ (Gate Resistance), $V_{GS}$ (gate-to-source voltage),
$V_{DS}$  (drain-to-source-voltage),  $I_{D_{max}}$  (peak  drain  current)  and
$V_{GS_{THR}}$ (gate threshold voltage).

The     maximum     drain     current     is     equal     to     the     peak
inductor    current    $I_{L_{1_{peak}}}$    as   calculated    in    equation
\ref{eq:circuit:buck:inductor_peak}: $I_{D_{max}}    =   I_{L_{1_{peak}}}    =
\SI{5.2}{\ampere}$

%\begin{equation}
%    I_{D_{max}} = I_{L_{1_{peak}}} = I_O + \left(\frac{V_{in}\cdot V_{out} - V_{out}^2}{2\cdot f_S \cdot L_1 \cdot V_{in}}\right) = \SI{5.2}{\ampere}
%    \label{eq:circuit:buck:mosfet_id}
%\end{equation}

The maximum  drain-to-source voltage $V_{DS}$  must be greater than  the input
voltage  $V_{in}  =  \SI{28}{\volt}$,  including  transients,   otherwise  the
MOSFETs will be damaged. MOSFETs with $V_{DS} = \SI{40}{\volt}$ were therefore
selected.

The  signals driving  the  gates of  the  MOSFETs have  a  maximum voltage  of
\SI{5}{\volt}  with  respect to  the  source.   During start-up  and  recovery
conditions, the gate drive signals  may be as low as \SI{3}{\volt}. Therefore,
to  ensure that  the  LT3741  recovers properly,  the  maximum gate  threshold
voltage should  be less than  \SI{2}{\volt}. For a robust design,  the maximum
gate-to-source voltage $V_{GS}$ should be greater than \SI{7}{\volt}.

Power losses in  the MOSFETs are related to  the on-resistance $R_{DS{(on)}}$,
the  transition losses  related to  the gate  resistance $R_G$,  gate-to-drain
capacitance  $Q_{GD}$  and  gate-to-source  capacitance  $Q_{GS}$. Power  loss
to  the  on-resistance  is  an  Ohmic  loss,  $I^2  R_{DS_{(on)}}$. The  power
loss  in  the  high  side  MOSFET $V_2$  can  be  approximated  with  equation
\ref{eq:circuit:buck:mosfet_ploss}.

\begin{multline}
    P_{LOSS} = (\textrm{ohmic loss}) + (\textrm{transission loss}) \\
             \approx \left( I_O^2 \cdot R_{DS_{(on)}} \cdot \rho_T \right)
                    + \left( \frac{V_{in} \cdot I_O}{\SI{5}{\volt}} \cdot \left(Q_{GD} + Q_{GS} \right) \cdot \left( 2 \cdot R_G + R_{PU} + R_{PD} \right) \cdot f_S \right) \\
    \label{eq:circuit:buck:mosfet_ploss}
\end{multline}
whereby   $\rho_T$   is  a   temperature-dependant   term   of  the   MOSFET's
on-resistance.  Using \SI{70}{\degree C} as the maximum operating temperature,
$\rho_T$  roughly equals  $1.3$.  $R_{PD}$  and $R_{PU}$  are the  LT3741 high
side  gate  driver  output   impedances,  \SI{1.3}{\ohm}  and  \SI{2.3}{\ohm},
respectively.

Driving the gates also causes power loss in switching MOSFETs.  The total gate
charge, $Q_G$, must be charged and discharged switch each switching cycle. The
power is  lost to the internal  LDO within the  LT3741. The power lost  to the
charging of the gates is:
\begin{equation}
    P_{LOSS\_LDO} \approx \left( (V_{in} - \SI{5}{\volt} \right) \cdot \left( Q_{GLG} + Q_{GHG} \right) \cdot f_S
    \label{eq:circuit:buck:switching_loss}
\end{equation}
whereby $G_{GLG}$ is the  low side gate charge and $Q_{GHG}$  is the high side
gate charge.

Table  \ref{tab:circuit:buck:mosfet}  in  appendix  \ref{appendix:mosfets}  on
page  \pageref{appendix:mosfets} lists  possible MOSFETs  that meet  the above
constraints.  For  each one  the power  losses $P_{LOSS}$  and $P_{LOSS\_LDO}$
were calculated. The  MOSFET which  ended up  being selected  is not  the best
model, but it is a lot cheaper than the best fit and has better documentation.
