% relevance/motivation
% problem statement
% approach: how is the problem solved
% results
% conclusions
% keywords

% introduction
% research problem
% body
% results
% conclusion

 % introduction
Emulating  solar  modules  in  a  laboratory  environment  currently  requires
expensive  and complex  equipment, hindering  development of  new solar  power
products. To  facilitate research  into  this area,  a  low-cost solution  for
emulating solar modules is required.

% approach
This report details our efforts in designing and constructing  a device for this
purpose.   We   developed   a   model  for  describing  solar  module   behavior
mathematically,  allowing both single-celled panels  as  well  as  more  complex
multi-celled panel configurations  to  be  described.  A  microcontroller  and a
voltage  converter  constitute  the  hardware  design.  The  microcontroller  is
responsible  for interacting with  the  outside  world,  while  the  converter's
purpose is to use the mathematical model  to  generate  the desired voltages and
currents on the device's output.

% results
At this point, the interface  and  most  of  the  circuitry  works  as intended.
Unfortunately,  due  to  a  design  error,  our  circuit  overloads  the voltage
converter, causing irreparable damage. Based on measurements and simulations, we
consider the likely cause to be overlong connections between  the  converter and
other components. The next step in finalising the device would  be  to  design a
new circuit board for fixing this issue.

